---
title: "linear model from Web"
author: "Andrew Valles Tovar"
date: "Spring 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```
  
The data shows a simulation on the arm strength expectation on the workers. Most of the points are centered around 50-100, which means it's expected for the workers to be around that arm strength.

### Numerical results
```{r}
cor(SIMS~ARM, data=data)
```
There is no difference on the correlation between SIMS and ARM. When the number is larger, the larger the correlation is between the two. The number is close to 1, so correspondence is minimal.

### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The equation of the line is SIMS=0.054563xARM-4.095160. The coefficient is positive, meaning the line increases and starts from the bottom left of the graph to the top right.

#### Predict at target point
```{r}
tgtpoint = data.frame(ARM = 88, GRIP = 94)
predict(model.1, tgtpoint, interval = c("prediction"))
```
This table shows the predicted target point is 0.7063836. At a 95% confidence interval, the value will be between -1.726209 and 3.138977.

#### scatterplot with model fit
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```  

This new scatter plot uses the predicted data calculated from the previous results. It shows where exactly on the graph the predicted data is expected to produce the expected results.

## Model 2 SIM~GRIP

### Now add in scatterplot
```{r}
basicGrip <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicGrip + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

The data shows a simulation on the grip strength expectation of workers. The points are mostly centered on the 100-150 grip range, with someone falling behind the middle of 50-100 and directly on the 100 range.

### Numerical results 
```{r}
cor(SIMS~GRIP, data=data)
```
For comparison, the SIMS vs ARMS numerical data is 0.6860073 and the one here is 0.6398458 for SIMS vs GRIP. SIMS vs ARMS is higher than SIMS vs GRIP, meaning SIMS vs ARMS is more accurate than the other due to SIMS vs GRIP having less correlation with a smaller value.

### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
``` 
Inferential data shows us the equation of the line which is SIMS=0.045463xGRIP-4.809675. The coefficient of the equation is positive, meaning it starts from the bottom left and ends near the top right of the graph.

#### predict model.2 at target point
```{r}
predict(model.2, tgtpoint, interval = c("prediction"))
```
The table shows the predicted target point is -0.5361543. The confidence level is 95%, so the value will be between -3.107961 and 2.035652.

#### now add the model fit to our plot for model.2
```{r}
basicGrip + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```   

Using the target point data from the previous calculation, the line shows where exactly on the graph the prediction is for best results. 

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

